---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  dpi = 300
)
```

# sdlhRTools: Personal package with custom functions for data visualization and analysis.

<!-- badges: start -->

<!-- badges: end -->

The R package *sdlhRTools* aims to collect in a single place auxiliary functions and customized data visualization tools that I use frequently when working with R. This package was born with the intention of personal use, but I try to keep and mantain a consistent and comprehensive documentation.

This is work continuously changing and under development. I welcome feedback, contributions and suggestions from users who may find anything useful here.

Happy plotting!

# Installation

The development version of this package is available to install from GitHub.

| Type        | Source | Command                                           |
|-------------|--------|---------------------------------------------------|
| Development | GitHub | `remotes::install_github("sergiodlash/sdlhRTools")` |


Once the installation is complete, you can load the package in your R scripts by using:

```{r}
library(sdlhRTools)
```

If you encounter any issues or have suggestions, please feel free to open an issue on the GitHub repository.

# Examples

## Themes

### sdlh

## Color Palettes

### Paimio Sanatorium

Color palette inspired in the Paimio Sanatorium by architect Alvar Aalto in Finland.

```{r paimio}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  labs(
    title = "Scatter Plot of Sepal Length vs Sepal Width",
    x = "Sepal Length",
    y = "Sepal Width"
  ) +
  scale_color_paimio(palette = "full", reverse = TRUE) +
  theme_sdlh()
```
### Ny Carlsberg Glyptotek

Color palette inspired in the Ny Calrsberg Glyptotek in Copenhagen.

```{r glyptotek}
ggplot(iris, aes(x = Species, y = Sepal.Width, fill = Species, color= Species)) +
  geom_violin( linewidth = 0) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', fill = "white", dotsize = 0.8, binwidth = 0.07)+
  labs(
    title = "Violin Plot of Sepal Width by Species",
    x = "Species",
    y = "Sepal Width"
  ) +
  scale_fill_glyptotek()+
  scale_color_glyptotek()+
  theme_sdlh()
```
